Figure 4 - Motifs

### 2024-08-06 ms_figure_4_motifs.Rmd
remove non-needed DBD info table from Fig4 and re-render html

---
title: "Figure 4 - Motifs"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    dbdtxt: "data/TF_DBD_annotation.txt"
    motifrds: "data/motifs_annotated.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    ncpu: 4
editor_options: 
    chunk_output_type: console
---

@@

```{r load-data}
# `dbd`: Transcription factor DNA binding domain information
dbd <- read.delim(params$dbdtxt) |>
    dplyr::mutate(cons = factor(ifelse(Conserved_human, "yes", "no"),
                                levels = c("yes", "no")),
                  DBD_class_simple = factor(
                      ifelse(DBD_class == "Zn(II)2Cys6", "Zn(II)2Cys6", "other"),
                      levels = c("other", "Zn(II)2Cys6")))

# `motifs`: table with annotated motif
motifs <- readRDS(params$motifrds)
motifs$altname <- motifs$name

>>>>

---
title: "Figure 4 - Motifs"
author: "Michael Stadler, Charlotte Soneson, Merle Skribbe"
date: "`r Sys.Date()`"
output: 
    html_document:
        theme: united
        toc: true
        toc_float: true
        code_folding: hide
params:
    motifrds: "data/motifs_annotated.rds"
    peakcsv: "data/fused_peaks_filtered.csv.gz"
    genomefasta: "reference/Schizosaccharomyces_pombe.ASM294v2.dna.toplevel.fa"
    ncpu: 4
editor_options: 
    chunk_output_type: console
---

@@

```{r load-data}
# `motifs`: table with annotated motif
motifs <- readRDS(params$motifrds)
motifs$altname <- motifs$name
